\section {Verbs Followed by \textit{-ing} with Examples}
\label{sec:Verbs-Followed-by-ing}
\begin{multicols}{2}
	\begin{itemize}
		\item avoid: I avoid eating junk food.
		\item enjoy: She enjoys reading novels.
		\item dislike: They dislike waking up early.
		\item suggest: He suggested going to the park.
		\item consider: We are considering moving to a new city.
		\item admit: She admitted stealing the money.
		\item finish: I finished doing my homework.
		\item miss: They miss traveling abroad.
		\item delay: He delayed replying to the email.
		\item deny: She denied breaking the vase.
		\item risk: They risk losing everything.
		\item imagine: Can you imagine living on the moon?
		\item recommend: I recommend trying this restaurant.
		\item practice: He practices playing the guitar every day.
		\item keep: She keeps asking the same question.
		\item quit: He quit smoking last year.
		\item mind: Do you mind opening the window?
		\item postpone: They postponed meeting until next week.
		\item involve: The job involves working long hours.
		\item escape: She escaped being caught by the police.
		\item resist: He couldn’t resist eating the cake.
		\item appreciate: I appreciate you helping me.
		\item tolerate: She tolerates working under pressure.
		\item spend: I spend hours cleaning the house.
		\item prefer: They prefer watching movies at home.
		\item endure: She endured running in the rain.
		\item anticipate: He anticipates winning the competition.
		\item mention: Did she mention going to the party?
		\item discuss: We discussed leaving early.
		\item complete: He completed painting the house.
		\item resume: They resumed working after the break.
		\item justify: She justified spending so much money.
		\item defer: He deferred taking the test until next month.
		\item excuse: Please excuse my arriving late.
		\item fancy: Do you fancy going out tonight?
		\item permit: They don’t permit smoking in this building.
		\item recall: I recall meeting him at the event.
		\item tolerate: He can’t tolerate being ignored.
	\end{itemize}
\end{multicols}
